Formalization of Abstract Rewriting

### 2025-02-12 Relations/Paper/Definitions.tex
update to defns

\begin{definition}
    An element $a \in A$ is \emph{$R$-weakly recurrent} ($WR_{R}$)if $a \mstep b$ for some recurrent element $b \in A$.

    A relation $R$ is weakly recurrent (WR) if every $a \in A$ is $R$-weakly recurrent.
\end{definition}

\begin{definition}
    An element $a \in A$ is \emph{$R$-strongly recurrent} ($SR_R$) if either $a$ itself is recurrent or every element one $R$ step
    from $a$ is also strongly recurrent.

    A relation $R$ is strongly recurrent (SR) if every
    $a \in A$ is $R$-strongly recurrent.
\end{definition}

@@

>>>>

\begin{definition}
    An element $a \in A$ is \emph{$R$-weakly minimal} ($WM_{R}$)if $a \mstep b$ for some minimal form $b \in A$.

    A relation $R$ is weakly minimal (WM) if every $a \in A$ is $R$-weakly minimal.
\end{definition}

\begin{definition}
    An element $a \in A$ is \emph{$R$-strongly minimal} ($SM_R$) if either $a$ itself is a minimal form or every element one $R$ step
    from $a$ is also strongly minimal.

    A relation $R$ is strongly minimal (SM) if every
    $a \in A$ is $R$-strongly minimal.
\end{definition}

@@

Definitions to add:
\begin{enumerate}
    \item Finite branching
    \item Any other terms from well foundedness
    \item The other terms we have for strongly 
\end{enumerate}
